### 2023-01-24 Manuscript/Draft1.Rmd
get Unicode to work for Chris (see https://bookdown.org/yihui/rmarkdown/pdf-document.html#latex-engine)

---
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
output:
  bookdown::pdf_document2:
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes
  pdf_document:
    toc: no
  word_document: default
  html_document: default
bibliography: IBMWG.bib
fontsize: 12pt
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
- \usepackage[belowskip=0pt,aboveskip=0pt]{caption}
 \usepackage{array}
 \usepackage{caption}
 \usepackage{graphicx}
 \usepackage{siunitx}
 \usepackage{colortbl}
 \usepackage{multirow}
 \usepackage{hhline}
 \usepackage{calc}
 \usepackage{tabularx}
 \usepackage{tabulary}
 \usepackage{threeparttable}
 \usepackage{wrapfig}
---

>>>>

---
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
output:
  bookdown::pdf_document2:
    latex_engine: xelatex
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes
  pdf_document:
    toc: no
  word_document: default
  html_document: default
bibliography: IBMWG.bib
fontsize: 12pt
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
- \usepackage[belowskip=0pt,aboveskip=0pt]{caption}
 \usepackage{array}
 \usepackage{caption}
 \usepackage{graphicx}
 \usepackage{siunitx}
 \usepackage{colortbl}
 \usepackage{multirow}
 \usepackage{hhline}
 \usepackage{calc}
 \usepackage{tabularx}
 \usepackage{tabulary}
 \usepackage{threeparttable}
 \usepackage{wrapfig}
---
